Irt plot extra

### 2022-07-03 manuscript.Rmd
rewrite Introduction add references in references.bib file adjustments in spelling and phrasing in Methods section #data collection

Our circadian rhythm is in sync with the earth's 24-hour rotation cycle. In this synchronization, light plays the vital role. Light sends signals to the master oscillator of our brain, the suprachiasmatic nuclei (SCN), via the third class of photoreceptors- intrinsically photosensitive retinal ganglion cells (ipRGCs) [@berson2002phototransduction; @lucas2014measuring; @provencio1998retinal], thus entraining our biological clock [@duffy2005entrainment]. However, the temporal properties of light exposure, i.e., the time of day and the duration of light exposure, play a vital role in our health and well-being. These influences of light are known as non-image-forming (NIF) effects of light and include several physiological and psychological aspects such as secretion of melatonin, modulation of pupil size, skin temperature, alertness and other higher cognitive functions [@cajochen2000dose; @lok2018light; @siraji2021effects]. Wrong light exposure at an inappropriate time of day may lead to sleep disturbances [@chellappa2013acute; @santhi2012spectral]. Evening and nighttime bright light exposure may cause suppression of melatonin [@gooley2011exposure] and may cause a phase shift in the internal biological clock, thus, desynchronizing the body clock with nature's day-night circle. This reorganization of the body clock can create a series of adverse effects, including alteration of rhythmicity of several hormones, increased stress, cancer, and metabolic disruption, including obesity, type II diabetes, and heart diseases [@navara2007dark]

With the increased use of electric light, the natural temporal organization of the dark-light cycle has been compromised. People are exposed to light more than ever. Furthermore, nighttime electric light exposure is significantly increased day by day. In the US, more than 80% of the population is exposed to a night sky that is brighter than nights with a full moon due to electric light at night [@navara2007dark]. Our circadian clock signals the start of our melatonin secretion in our body based on the darkness of the night [@pauley2004lighting]. Since nights are no longer pure dark, most of the light-dependent systems of our body are disrupted. For example, studies suggest that electric monochromatic blue light exposure as low as 0.1 lux, which is almost equivalent to the brightness of full moonlight, may reduce the melatonin level [@brainard2002photoreception]. In turn, such changes in melatonin levels influence metabolism, immunity, fertility, and other hormonal balance, including adrenaline and thyroid hormone [@prendergast2002mammalian].

In recent years, the focus has been given in understanding the pathways underlying these influences of light. ipRGCs are mostly responsible for signalling the SCN when the ambient light changes [@gooley2003broad]. Additionally, ipRGCs also send signals to different brain regions, closely associated with our sleep, attention and emotion, thus influencing our work performance, sleep quality and mood (For a detailed discussion, see [@lok2018light; @siraji2021effects]). However, it is also essential to understand the behaviours people are engaging in, which ultimately quantify our light consumption. People are getting different types of light exposure due to their different daily life activities, including workplace habits, bedtime hygiene,  pastimes, and other social activities. Currently, little effort has been made to understand and capture these behaviours. Supplementary Table 1 summarizes relevant questionnaires to understand different light exposure related properties. Only a few questions of these questionnaires were related to light exposure related behaviour. For example, "Munich Chronotype Questionnaire" [@roenneberg2003life], a self-reporting chronotype identifier, has questions about time spent outdoors and the work environment. Popularly used "Pittsburgh Sleep Quality Index" [@buysse1989pittsburgh], a measure of sleep quality, also has questions about sleeping and wake-up time. However, none of these questionnaires provides a scaleable solution to capture light exposure related behaviour. To fill this gap, here we have reported the development process of a novel tool- "Light Exposure Behavior Assessment" (LEBA), to capture and quantify different light exposure related behaviour. LEBA will allow us to capture different light exposure related behaviour and gain insight into how different behaviour changes one's light exposure. Understanding these light exposure related behaviour will help us provide a personalized light diet to decrease the effects of inappropriate light exposure.

@@

A quantitative cross-sectional fully anonymous geographically unconstrained online large-scale survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch). Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic-book "Enlighten your clock" co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux]. The landing page of the online survey had the explanatory statements where we mentioned participation was voluntary and that respondents could withdraw from participation at any time without being penalized. At the beginning of the survey, for the adult participants (\>18 years) consent was recorded digitally. Under-aged participants (\<18 years) were urged to obtain assent from their parents/legal guardians. The entire survey was estimated to take less than 30 minutes. Participants were not compensated. As a part of the demographic information participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language. The demographic characteristics of our sample are given in Table 1. To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention. What is 4+5?"). Participants were asked to confirm that they were participating in the survey for the first time. Questions incorporating retrospective recall were all aligned to the period of "past four weeks".

We conducted two rounds of data collection. At first, we collected data from `r nrow(EFA.descriptives)` participants (EFA sample). In the second round we collected data from another `r nrow(CFA.descriptives)` participants (CFA sample) making a total sample of `r nrow(desctable.data)`. The data analysed in this study was collected between 17 May 2021 and 3 September 2021.

@@

Figure \@ref(fig:FlowchartFig) summarizes the steps we followed while developing LEBA. In our analysis we used R statistical tool [@R-base]. **First**, we developed an item pool of 48 items with six-point Likert type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial scale. Our purpose was to capture light exposure related behaviour. In that context, the first two response options: "Does not apply/I don't know" and "Never" were providing similar information. As such we collapsed them into one, making it a 5 point Likert type response format (1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always).

**Second**, for data collection we conducted two rounds of large-scale survey. **Third**, as a part of psychometric analysis, we conducted descriptive and item analysis and proceeded to the exploratory factor analysis (EFA) using "psych" package [@R-psych] on the data collected in the first round (EFA sample; n=`r nrow(EFA.descriptives)`). Prior to the EFA, necessary assumptions, including sample adequacy, normality assumptions, quality of correlation matrix were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, in EFA we used polychoric correlation matrix and employed principal axis (PA) as the factor extraction method [@desjardinsHandbookEducationalMeasurement2018; @watkinsStepbyStepGuideExploratory2020]. We used a combination of factor identification method including Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers. To determine the latent structure, we followed the common guidelines : (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading \> .3 across factors [@bandalosFactorAnalysisExploratory2018]. <!-- We also conducted an EFA on non-merged response options data set (**Supplementary File 1**). -->

For reliability estimation "psych" package was used [@R-psych]. Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it has a tendency to deflate the estimates for Likert-type data since the calculation is based on Pearson-correlation matrix which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal]. Subsequently to get better estimates of reliability we reported ordinal alpha for each factors obtained in EFA [@zumbo2007ordinal]. We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$ coefficient which is a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use]. Both ordinal alpha and McDonald's $\omega_t$ coefficient value range between 0 to 1 and higher value represents better reliability.

To validate the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with weighted least square with mean and variance adjusted (WLSMV) estimator [@desjardinsHandbookEducationalMeasurement2018] using "lavaan" package [@R-lavaan] on the data collected in the second round (CFA sample; n=`r nrow(CFA.descriptives)`). We assessed the model fit using common model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI): close to .95 or above/ between .90-.95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner]. However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015] and SRMR does not work well with ordinal data [@RN1272] As such, we judged the model fit using CFI, TLI and RMSEA.

@@

Table 1 summarizes the survey participants' demographic characteristics. Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. (XX??) participants were excluded from analysis due to not passing at least one of the "attention check" items. For EFA, a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]. To assess sampling adequacy for CFA, we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per item is required to earn trustworthiness of the result. Both our EFA and CFA sample size exceeded these requirements. We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones). Participants reported a diverse range of geographic location Participants indicated filling out the online survey from a diverse range of geographic locations. For a complete list of geographic locations, see **Supplementary Table 2**.

@@

Figure \@ref(fig:efagtPic1) and Figure \@ref(fig:efagtPic2) summarize the response pattern of our total sample (n=`r nrow(sem.data)`) for all 48 items. Most of the items appeared skewed. The Shapiro–Wilk test of univariate normality [@shapiroAnalysisVarianceTest1965] and Mardia test of multivariate normality [@mardiaMeasuresMultivariateSkewness1970] indicated our data violated both univariate and multivariate normality. Multivariate skew was `r printnum(mardia.all.data$b1p)` (p \<0.001) and multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p \<0.001).

@@

**Supplementary Figure 1** summarizes the univariate descriptive statistics for the 48 items in the EFA sample (n=`r nrow(EFA.data)`). Here also our data violated univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970]. Multivariate skew was `r printnum(mardia$b1p)` (p \<0.001) and multivariate kurtosis was `r printnum(mardia$b2p)` (p \<0.001). The corrected item-total correlation ranges between `r apa(low.r.corec,2,F)` -`r apa(high.r.corec,2,F)`. However, no item was discarded based on descriptive statistics or item analysis.

@@

Table \@ref(tab:tabCfa) summarizes the CFA fit indices of our fitted model. Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`; RMSEA = `r apa(fit.1[7],2,F)` [`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep] and 16-17 [item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day]. Item pair 32-33 stemmed from the preference of dimming electric device's brightness before bed time and item pair 16-17 stemmed from the preference of using blue filtering or coloured glasses during the daytime. Given the similar nature of behaviour these item pair were capturing, we accepted the equity constrain imposed. Nevertheless, SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`).

@@

In our CFA sample we had `r mi.count[1,2]` native English speakers and `r mi.count[2,2]` non-native English speakers. **Supplementary Table 5** summarizes the demographic descriptions native and non-native English speakers. Table \@ref(tab:InvarianceTab) indicates our fitted model had acceptable fit indices for all of the fitted MI models. The model fit did not significantly decrease across the nested models indicating the acceptability of the highest measurement invariance model: residual model.

@@

**Supplementary Table 7** summarizes the item fit indexes of the 18 items. All items had RMSEA value $\le$.06 indicating adequate fit of the items to the fitted IRT model. **Supplementary Figure 4** depicts the person fit Zh statistics histogram of our fitted models. Zh statistics are larger than -2 for most participants, suggesting a good person fit of the selected IRT models.

>>>>

Light exposure received by the eyes affects many facets of human health, well-being, and performance beyond visual sensation and perception [@boyce_light_2022]. The so-called non-image-forming (NIF) effects of light comprise light’s circadian and non-circadian influence on several physiological and psychological functions, such as the secretion of melatonin, sleep, mood, pupil size, body temperature, alertness, and higher cognitive functions [i.a. reviewed in @Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020 ].
With the introduction of artificial electric light, human behaviour has become somewhat independent of the natural light-dark cycle – people can now frequently choose when to be exposed to light or darkness. For example, they can decide whether to go outdoors and seek out sunlight, switch on/off light-emitting devices, use certain types of lights at home, or avoid specific light environments altogether. Additionally, when light sources can not be directly manipulated, sought out, or avoided (for example, at school, work, or in public places), there is still potential leeway to influence them behaviourally, for instance, by wearing sunglasses, directing one’s gaze away or supplementing the situation with additional light sources. Although clearly yielding the potential for good, this agency is further associated with increased electric light exposure at night and indoor time during the day, compromising the natural temporal organisation of the light-dark cycle. For example, in the US, an average of 87% of the time is spent in enclosed buildings [@Klepeis.2001], and more than 80% of the population is exposed to a night sky that is brighter than nights with a full moon due to electric light at night [@navara_dark_2007].
An extensive body of scientific evidence suggests that the imbalance of light and dark exposure disrupts humans’ light-dependent physiological systems [@Lunn.2017]. This, in turn, gives rise to a series of adverse health consequences, including the alteration of several hormonal rhythms, increased cancer rates, cardiovascular diseases, and metabolic disorders, such as obesity, and type II diabetes [see reviews by @Lunn.2017; @navara2007dark; @Chellappa.2019]
These findings have sparked a significant call for assessment and guidance regarding healthy light exposure and timing – the latter was recently published as consensus-based experts’ recommendations, postulating specific requirements for indoor light environments during the daytime, evening, and nighttime [@Brown.2022]. Furthermore, building on earlier attempts [e.g. @hubalek_ambulant_2006], there was a recent push toward the development and use of portable light loggers to improve ambulant light assessment and gain more insight into the NIF effects of light on human health in field conditions [@stampfli_light-dosimeter_2021; @van_duijnhoven_recommendations_2017; @webler_towards_2021]. Attached to different body parts (e.g., wrist, head on eye level, chest), these devices allow objectively measuring personal light exposure under real-world conditions and are valuable tools for field studies. Nevertheless, these devices also encompass limiting factors such as potentially being intrusive (e.g., when eye-level worn), yielding the risk of getting covered (e.g., when wrist- or chest-worn) and requiring (monetary) resources and expertise for acquisition and maintenance of the devices.
On the other hand, several attempts have been made to quantify received light exposure subjectively with self-report questionnaires (cf. **Supplementary Table 1**), bypassing the cost and intrusiveness issues. However, subjective light intensity assessments pose a new set of challenges: The human visual system constantly adapts to brightness [@hurvich_perception_1966], while the human non-visual light processing works largely subconsciously [@allen_exploiting_2018], making the self-report assessment of light properties potentially quite challenging, especially for inexperienced laypeople. Retrospectively recalling the properties of a light source can further complicate such subjective evaluations. Moreover, measuring light properties alone does not yield any information about how individuals might behave differently regarding diverse light situations. These measurement limitations point to a couple of research challenges we aim to take on here: How can we gain insight into light exposure patterns via self-report but circumvent directly inquiring about the specific properties and intensity of a light source? And how can we simultaneously assess how people habitually interact with the received light?
We propose that these challenges can be tackled by assessing light-exposure-related behaviour. We argue that, besides measuring received light exposure as intensity, it is also essential to understand people's behaviours concerning different light situations. Since, in many cases, humans have become their own agents regarding their exposure to light or darkness through artificial electric light, people's light exposure-related behaviours ultimately determine their light consumption and timing: People receive different light depending on their daily activities, including workplace habits, bedtime hygiene, pastime and social activities. The final objective of changing light-dark exposure patterns to avoid or mitigate negative health consequences from unhealthy habits will not just need an assessment of the lighting properties but the active change of behaviours related to light exposure. We argue that assessing these activities is a beneficial stepping stone for prospective behaviour change. Furthermore, people without light measurement expertise may find it easier to appraise and recall their behaviour concerning light exposure than subjectively assessing a light source’s properties.
To date, little effort has been made to understand and capture these activities. **Supplementary Table 1** summarises the existing questionnaire literature assessing light exposure-related properties. However, only a few questions of these existing tools were associated with light exposure-related behaviour. For example, the “Munich Chronotype  Questionnaire” [MCTQ; @roenneberg2003life], a popular self-report tool for identifying chronotypes via mid-sleep times, includes questions about the individual’s time spent outdoors on workdays and free days. In addition, the “Pittsburgh Sleep Quality Index” [PSQI; @buysse1989pittsburgh], a popular measure of sleep quality, contains questions about sleep and wake-up times, which are relevant to the light exposure around bedtime. However, none of these questionnaires provides a scaleable solution to capture light exposure-related behaviour in various physiologically relevant lighting scenarios.
To fill this gap, we here present the development process of a novel self-report tool - the “Light Exposure Behavior Assessment” (LEBA) - for capturing and quantifying diverse light exposure-related behaviours.

@@

A quantitative cross-sectional fully anonymous, geographically unconstrained online large-scale survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch). Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic book "Enlighten your clock", co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by the distribution of the survey link via f.lux [@f.lux]. The initial page of the online survey provided information about the survey including that participation was voluntary and that respondents could withdraw from participation at any time without being penalised. Following this information sheet, consent was recorded digitally for the adult participants (\>18 years), whereas under-aged participants (\<18 years) were prompted to obtain additional assent from their parents/legal guardians. Filling in the entire survey was estimated to take less than 30 minutes, and participation was not compensated.
As a part of the demographic information, participants provided information regarding age, sex, gender identity, occupational status, COVID-19-related occupational setting, time zone/country of residence and native language. The demographic characteristics of our sample are given in **Table 1**. Additionally, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention. What is 4+5?"), to ensure high data quality and participants were asked to confirm that they participated in the survey for the first time. All questions incorporating retrospective recall were aligned to a "past four weeks" period.

We collected the survey data between 17 May 2021 and 3 September 2021 – firstly from `r nrow(EFA.descriptives)` participants (EFA sample) – and subsequently, another dataset from `r nrow(CFA.descriptives)` participants (CFA sample) totalling `r nrow(desctable.data)`.

@@

Figure \@ref(fig:FlowchartFig) summarises the steps we followed while developing LEBA. We conducted all analyses with the statistical software environment R [@R-base]. 
Firstly, we set an item pool of 48 items with a six-point Likert-type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial scale. Our purpose was to capture light exposure-related behaviour. In that context, the first two response options: "Does not apply/I don't know" and "Never" provided similar information. As such we collapsed them into one, making it a 5-point Likert-type response format (1-Never, 2-Rarely, 3-Sometimes, 4-Often, 5-Always).

After the two rounds of data collection, we conducted descriptive and item analysis and proceeded to the exploratory factor analysis (EFA) using "psych" package [@R-psych] on the data collected in the first round (EFA sample; n=`r nrow(EFA.descriptives)`), as a part of psychometric analysis. Prior to the EFA, the necessary assumptions, including sample adequacy, normality assumptions, quality of correlation matrix were assessed. As our data violated both the univariate and multivariate normality assumption and yielded ordinal response data, we used polychoric correlation matrix in the EFA and employed principal axis (PA) as the factor extraction method [@desjardinsHandbookEducationalMeasurement2018; @watkinsStepbyStepGuideExploratory2020]. We used a combination of factor identification method including Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers. To determine the latent structure, we followed the common guidelines: (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading \> .3 across factors [@bandalosFactorAnalysisExploratory2018]. <!-- We also conducted an EFA on non-merged response options data set (**Supplementary File 1**). -->

For reliability estimation, the "psych" package was applied [@R-psych]. Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it has a tendency to deflate the estimates for Likert-type data since the calculation is based on the Pearson-correlation matrix, which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal]. Subsequently, to get better reliability estimates, we reported ordinal alpha for each factor obtained in the EFA [@zumbo2007ordinal]. We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$ coefficient, which was suggested as a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use]. Both ordinal alpha and McDonald's $\omega_t$ coefficient values range between 0 to 1, where higher values represent better reliability.

To validate the latent structure obtained in the EFA, we conducted a categorical confirmatory factor analysis (CFA) with the weighted least squares means and variance adjusted (WLSMV) estimation [@desjardinsHandbookEducationalMeasurement2018], using the "lavaan" package [@R-lavaan] on the data collected in the second round (CFA sample; n=`r nrow(CFA.descriptives)`). We assessed the model fit using common model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI): close to .95 or above/ between .90-.95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner]. However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015] and SRMR does not work well with ordinal data [@RN1272] As such, we judged the model fit using CFI, TLI and RMSEA.

@@

Table 1 summarises the survey participants' demographic characteristics. Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. (XX??) participants were excluded from analysis due to not passing at least one of the "attention check" items. For EFA, a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]. To assess sampling adequacy for CFA, we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per item is required to earn trustworthiness of the result. Both our EFA and CFA sample size exceeded these requirements. We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones). Participants reported a diverse range of geographic location Participants indicated filling out the online survey from a diverse range of geographic locations. For a complete list of geographic locations, see **Supplementary Table 2**.

@@

Figure \@ref(fig:efagtPic1) and Figure \@ref(fig:efagtPic2) summarise the response pattern of our total sample (n=`r nrow(sem.data)`) for all 48 items. Most of the items appeared skewed. The Shapiro–Wilk test of univariate normality [@shapiroAnalysisVarianceTest1965] and Mardia test of multivariate normality [@mardiaMeasuresMultivariateSkewness1970] indicated our data violated both univariate and multivariate normality. Multivariate skew was `r printnum(mardia.all.data$b1p)` (p \<0.001) and multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p \<0.001).

@@

**Supplementary Figure 1** summarises the univariate descriptive statistics for the 48 items in the EFA sample (n=`r nrow(EFA.data)`). Here also our data violated univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970]. Multivariate skew was `r printnum(mardia$b1p)` (p \<0.001) and multivariate kurtosis was `r printnum(mardia$b2p)` (p \<0.001). The corrected item-total correlation ranges between `r apa(low.r.corec,2,F)` -`r apa(high.r.corec,2,F)`. However, no item was discarded based on descriptive statistics or item analysis.

@@

Table \@ref(tab:tabCfa) summarises the CFA fit indices of our fitted model. Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`; RMSEA = `r apa(fit.1[7],2,F)` [`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep] and 16-17 [item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day]. Item pair 32-33 stemmed from the preference of dimming electric device's brightness before bed time and item pair 16-17 stemmed from the preference of using blue filtering or coloured glasses during the daytime. Given the similar nature of behaviour these item pair were capturing, we accepted the equity constrain imposed. Nevertheless, SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`).

@@

In our CFA sample we had `r mi.count[1,2]` native English speakers and `r mi.count[2,2]` non-native English speakers. **Supplementary Table 5** summarises the demographic descriptions native and non-native English speakers. Table \@ref(tab:InvarianceTab) indicates our fitted model had acceptable fit indices for all of the fitted MI models. The model fit did not significantly decrease across the nested models indicating the acceptability of the highest measurement invariance model: residual model.

@@

**Supplementary Table 7** summarises the item fit indexes of the 18 items. All items had RMSEA value $\le$.06 indicating adequate fit of the items to the fitted IRT model. **Supplementary Figure 4** depicts the person fit Zh statistics histogram of our fitted models. Zh statistics are larger than -2 for most participants, suggesting a good person fit of the selected IRT models.
